---
title: "Problem Set 2 - Solutions"
output: rmdformats::readthedown
css: custom.css
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = TRUE)
```

```{r}
library(tidyverse)
library(shiny)
library(lubridate)
my_theme <- theme_bw() +
  theme(
    panel.background = element_rect(fill = "#f7f7f7"),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(),
    plot.background = element_rect(fill = "transparent", colour = NA)
  )
theme_set(my_theme)
```


# Interactive German Traffic 

## Scoring

* a - b, Design (1 points): Creative and readable (1 point), generally appropriate but with some lack of critical attention (.5 points), difficult to read (0 points)
* a - b, Code (0.5 points): Clear and concise (0.5 points), correct but unnecessarily complex (0.25 points), missing (0 points)
* c, Design and Discussion (1 points): Creative question, solution, and
interpretation (1 point), appropriate question, solution, and interpretation,
but perhaps simplistic question / difficult to read design / underdeveloped
interpretation (0.5 points), misleading design or no interpretation (0 points)
* c, Code (0.5 points): Clear and concise (0.5 points), correct but unnecessarily complex (0.25 points), missing (0 points)

## Question

This problem will revisit the previous problem from an interactive point of
view. We will build a visualization that helps users explore daily traffic
patterns across multiple German cities, using interactivity to help users
navigate the collection. We will need additional features related to the day of
the week for each timepoint, created by the `wday` function below,

```{r}
traffic <- read_csv("https://uwmadison.box.com/shared/static/x0mp3rhhic78vufsxtgrwencchmghbdf.csv") %>%
 mutate(day_of_week = wday(date))
```


## Example Solution

a. Design and implement a Shiny app that allows users to visualize traffic
over time across selected subsets of cities. Make sure that it is possible
to view data from more than one city at a time. It is not necessary to label
the cities within the associated figure.

    We first define a function that, when given a subset of cities, draws a line
  plot.

    ```{r, eval = FALSE}
    plot_traffic <- function(df) {
      ggplot(df) +
        geom_line(aes(date, value, group = name)) +
        labs(x = "Date", y = "Traffic") +
        theme(axis.title = element_text(size = 20))
    }
    ```
  
    Our design will update a time series plot of all the cities every time a
  dropdown menu is updated. We will allow multiple cities to be selected
  simultaneously. Specifically, our UI has an input for choosing cities and
  displays the line plot as an output. Our server recognizes changes in the
  choice of cities, filters the data to that subset, and then draws the updated
  time series.
    
    ```{r, eval = FALSE}
    ui <- fluidPage(
      selectInput("city", "City", unique(traffic$name), multiple = TRUE),
      plotOutput("time_series")
    )
    
    server <- function(input, output) {
      output$time_series <- renderPlot({
        traffic %>%
          filter(name %in% input$city) %>%
          plot_traffic()
      })
    }
    
    shinyApp(ui, server)
    ```
    
<iframe src="https://data-viz.it.wisc.edu/content/da978e9a-126c-4319-abcf-ce5b3fefadc3" width=900 height=550 data-external="1"/>

b. Introduce new inputs to allow users to select a contiguous range of days
of the week. For example, the user should have a way of zooming into the
samples taken within the Monday - Wednesday range.

    We use nearly the same design except that a new slider input is provided for
    choosing days of the week. When a range of days is chosen, then the time
    series will show only that range for the currently selected cities.

    ```{r, eval = FALSE}
    ui <- fluidPage(
      selectInput("city", "City", unique(traffic$name), multiple = TRUE),
      sliderInput("day_of_week", "Days", 2, 7, c(2, 7)),
      plotOutput("time_series")
    )
    
    server <- function(input, output) {
      output$time_series <- renderPlot({
        traffic %>%
          filter(
            name %in% input$city, 
            day_of_week >= input$day_of_week[1] & day_of_week <= input$day_of_week[2]
          ) %>%
          plot_traffic()
      })
    }
    
    shinyApp(ui, server)
    ```
    
<iframe src="https://data-viz.it.wisc.edu/content/aa7c25b0-618f-41a2-80b7-1816c6ea9b41" width=900 height=550 data-external="1"/>

c. Propose, but do not implement, at least one alternative strategy for
supporting user queries from either part (a) or (b). What are the tradeoffs
between the different approaches in terms of visual effectiveness and
implementation complexity?

    One alternative implementation could use a graphical query (instead of a
    dropdown menu) to select cities of interest. We could show the cities as a
    scatterplot on a map, with circle size reflecting their average weekly
    traffic level. By brushing cities on the map, we could update the currently
    displayed time series.
    
    This approach would be more effective for multiple cities that are
    geographically close by. It could also guide users towards cities that have
    higher vs. lower traffic levels, to see if they have any systematic
    differences. It would be less effective if the cities that we would want to
    compare with one another are not geographically close (in that case, we
    might imagine using another feature of the cities to guide the query).
    
    The implementation becomes somewhat more complex, because we would have to
    use a brush query and implement a map. If users are familiar with the
    locations of the cities, and if spatial queries are of genuine interest,
    then this additional cost might be worthwhile.

# NYC Rentals

## Scoring

* a Design and code (0.5 points): Correct and polished static visualization (0.5
points), correct visualization but in need of refinement (0.25 points), missing
or difficult to read visualization (0 points).
* b Design and code (1 point): Clear and effective visual design and
implementation (0.5 points), correct but not refined design or implementation
(0.25 points), messy or unclear design or implementation (0 points).
* c (1 point). Same criteria as part (b).
* d Discussion (0.5 points): Correct and well-developed interpretation (0.5
points), correct but somewhat underdeveloped (0.25 points), missing or incorrect
interpretations (0 points).

## Question

In this problem, we'll create a visualization to dynamically query a
[dataset](https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv)
of Airbnb rentals in Manhattan in 2019. The steps below guide you through the
process of building this visualization.

## Example Solution

a. Make a scatterplot of locations (Longitude vs. Latitude) for all the rentals,
colored in by `room_type`.

    The main logic for this figure is given in the `ggplot` and `geom_point`
    layers below. We use `scale_color_manual` to create a custom color scheme, a
    `guide_legend` to allow the legend points to stand out more clearly than the
    scatterplot points, and `coord_fixed` to keep longitude and latitude
    coordinates in proportion with one another.

    ```{r}
    rentals <- read_csv("https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv")
    ggplot(rentals) +
      geom_point(aes(longitude, latitude, col = room_type), size = 0.3, alpha = 0.6) +
      scale_color_manual(values = c("#3F4B8C","#F26444", "#40331D")) +
      guides(col = guide_legend(override.aes = list(alpha = 1, size = 2))) +
      labs(col = "Room Type") +
      coord_fixed() +
      theme_void()
    ```
    
b. Design a plot and a dynamic query so that clicking or brushing on the
plot updates the points that are highlighted in the scatterplot in (a). For
example, you may query a histogram of prices to focus on neighborhoods that
are more or less affordable.

    We will implement the suggested design, using a brushed histogram to
    highlight all the units within a specified price range. The map will always
    show all points, but their size and opacity will be updated to reflect the
    brush selection.

    ```{r, eval = FALSE}
    ui <- fluidPage(
      h3("NYC Airbnb Rentals"),
      fluidRow(
        column(6,
               plotOutput("histogram", brush = brushOpts("plot_brush", direction = "x"), height = 200),
               dataTableOutput("table")
        ),
        column(6, plotOutput("map", height = 600)),
      ),
      theme = bs_theme(bootswatch = "minty")
    )
    
    server <- function(input, output) {
      selected <- reactiveVal(rep(TRUE, nrow(rentals)))
      observeEvent(input$plot_brush, {
        selected(brushedPoints(rentals, input$plot_brush, allRows = TRUE)$selected_)
      })
      
      output$histogram <- renderPlot(overlay_histogram(rentals, selected()))
      output$map <- renderPlot(scatterplot(rentals, selected()))
      output$table <- renderDataTable(filter_df(rentals, selected()))
    }
    
    shinyApp(ui, server)
    ```
    
    We have encapsulated the code for updating the plots into separate
    functions, printed below. We make sure that both the histogram and
    scatterplot highlight the currently selected range. This is the reason for
    using two `geom_histogram` layers in `overlay_histogram` -- one layer is
    needed for the context and a second is used for the currently highlighted
    selection.
    
    ```{r, eval = FALSE}
    scatterplot <- function(df, selected_) {
      df %>%
        mutate(selected = selected_) %>%
        ggplot() +
        geom_point(
          aes(
            longitude, latitude, col = room_type, 
            alpha = as.numeric(selected),
            size = as.numeric(selected)
          )
        ) +
        scale_color_manual(values = c("#3F4B8C","#F26444", "#40331D"), guide = "none") +
        scale_alpha(range = c(0.1, .5), guide = "none") +
        scale_size(range = c(0.1, .9), guide = "none") +
        coord_fixed() +
        theme_void()
    }
    
    overlay_histogram <- function(df, selected_) {
      sub_df <- filter(df, selected_)
      ggplot(df, aes(trunc_price, fill = room_type)) +
        geom_histogram(alpha = 0.3, binwidth = 25) +
        geom_histogram(data = sub_df, binwidth = 25) +
        scale_y_continuous(expand = c(0, 0, 0.1, 0)) +
        scale_fill_manual(values = c("#3F4B8C","#F26444", "#40331D")) +
        labs(
          fill = "Room Type",
          y = "Count",
          x = "Price"
        )
    }
    
    filter_df <- function(df, selected_) {
      filter(df, selected_) %>%
        select(name, price, neighbourhood, number_of_reviews) %>%
        rename(Name = name, Price = price, Neighborhood = neighbourhood, `Number of Reviews` = number_of_reviews)
    }
    ```
  
  <iframe src="https://data-viz.it.wisc.edu/content/b31a14ea-20dd-4718-b2e9-39bc318a2306" width=900 height=550 data-external="1"/>
  
c. Implement the reverse graphical query. That is, allow the user to update
the plot in (b) by brushing over the scatterplot in (a).
  
    We can use almost exactly the same code as in the above app. The only
    difference is that we add a brush to our map. By keeping the brush IDs the
    same across the two `plotOutput`s, we ensure that the plot is updated
    whenever either brush is changed.
    
    ```{r eval = FALSE}
    ui <- fluidPage(
      h3("NYC Airbnb Rentals"),
      fluidRow(
        column(6,
               plotOutput("histogram", brush = brushOpts("plot_brush", direction = "x"), height = 200),
               dataTableOutput("table")
        ),
        column(6, plotOutput("map", brush = "plot_brush", height = 600)),
      ),
      theme = bs_theme(bootswatch = "minty")
    )
    ```
    
<iframe src="https://data-viz.it.wisc.edu/content/a410cc0e-84a1-46f6-959d-1c8cfbb2c729" width=900 height=550 data-external="1"/>
  
d. Comment on the resulting visualization(s). If you had a friend who was
interested in renting an Airbnb in NYC, what would you tell them?
      
    There are many ways you could interpret this visualization to guide the
    selection of rentals. If your friend were looking for more affordable units,
    you could direct them to units uptown, but with the caveat that they would
    be more likely to be shared (rather then a rental for the entire apartment).
  
# Random Point Transitions
  
## Scoring

a. Code (1 point): Concise and effectively discussed implementation using
`.enter()` and `.append()` (1 point), correct but complex or unjustified
implementation (0.5 points), incorrect or poorly explained implementation (0
points).
b. Code (1 point): Correct and concise extension of part (a) (1 point),
technically correct but could be further refined or discussed (0.5 points), in
correct or insufficiently discussed (0 points).
c. Code and Design (1 point): Creative implementation that builds naturally from
part (b) (1 point), appropriate implementation but could be refined (0.5 point),
missing or poorly explained implementation (0 points).

## Question
This exercise will give practice implementing
transitions on simulated data. The code below generates a random set of 10
numbers,

```{d3, eval = FALSE}
let generator = d3.randomUniform();
let x = d3.range(10).map(generator);
```

## Example Solution

a. Encode the data in `x` using the x-coordinate positions of 10 circles.

    The D3 code for this encoding must bind the data and then set the `cx`
    attribute according to the current data value. Note that the radius and `cy`
    attributes did not  have to be set here -- since they are constant across
    all data elements, we put their values into the CSS file.
    
    ```{r, eval = FALSE}
    let generator = d3.randomUniform();
    let x = d3.range(10).map(generator);
    
    d3.select("svg")
      .selectAll("circle")
      .data(x).enter()
      .append("circle")
      .attr("cx", d => 900 * d)
    ```

    We had used the following HTML and CSS, which are similar to all the
    examples used in class. They are just an empty SVG on a page that loads the
    required resources.

    HTML:
    ```{r, eval = FALSE}
    <!DOCTYPE html>
    <html>
      <head>
        <script src="https://d3js.org/d3.v7.min.js"></script>
        <script src="https://d3js.org/d3-selection-multi.v1.min.js"></script>
        <link rel="stylesheet" href="q3.css">
      </head>
      <body>
        <svg height=500 width=900>
        </svg>
      </body>
      <script src="q3a.js"></script>
    </html>
    ```
    
    CSS:
    ```{r, eval = FALSE}
    circle {
      cy: 250;
      r: 20
    }
    ```

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3a.html" width=900 height=550 data-external="1"/>

b. Animate the circles. Specifically, at fixed time intervals, generate a
new set of 10 numbers, and smoothly transition the original set of circles
to locations corresponding to these new numbers.
    
    We add the following lines to the javascript in part (a). This is creating a
    new `x` array and transitioning the points to a new `cx` based on the newly
    bound data. We create the animation by repeatedly calling `update` using
    `d3.interval()`.
    
    ```{r, eval = FALSE}
    function update() {
      x = d3.range(10).map(generator);
      d3.selectAll("circle")
        .data(x)
        .transition()
        .duration(1000)
        .attrs({
          cx: d => 900 * d,
        })
    }
    
    d3.interval(update, 1000)
    ```

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3b.html" width=900 height=550 data-external="1"/>

c. Extend your animation so that at least one other attribute is changed at
each time step. For example, you may consider changing the
color or the size of the circles. Make sure that transitions remain smooth
(e.g., if transitioning size, gradually increase or decrease the circles'
radii).

    We modify our `.attrs` function above to set random radii and colors. Note
    that we had to remove `r` from the CSS in part (a) to ensure that it doesn't
    overrule our D3-defined `r` attribute.
    
    ```{r, eval = FALSE}
    .attrs({
      cx: d => 900 * d,
      r: d => 50 * generator(),
      fill: d => `hsl(${360 * generator()},${100 * generator()}%,${20 + 80 * generator()}%)`
    })
    ```

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3c.html" width=900 height=550 data-external="1"/>

# Bar Chart Transitions

## Scoring

* Code (2 points): Clear and concise code (0.5 points), correct but
unnecessarily complex (0.25 points), missing (0 points).
* Completeness (2 points): Implements all required functionality (2 points),
implements most requirements (1 point), fails to implement key functionality (0
points).

## Question

This problem continues [Simple Bar Chart] above. We will create a bar chart that
adds and removes one bar each time a button is clicked. Specifically, the
function below takes an initial array `x` and creates a new array that removes
the first element and adds a new one to the end. Using D3’s generate update
pattern, write a function that updates the visualization from [Simple bar chart]
every time that `update_data()` is called. New bars should be entered from the
left, exited from the right, and transitioned after each click. Your solution
should look (roughly) like [this example](https://github.com/krisrs1128/stat679_code/blob/main/activities/week5/simple_bars_example.mov?raw=true).

```{d3, eval = FALSE}
let bar_ages = [],
generator = d3.randomUniform(0, 500),
id = 0;

function update() {
  bar_ages = bar_ages.map(d => { return {id: d.id, age: d.age + 1, height: d.height }})
  bar_ages.push({age: 0, height: generator(), id: id});
  bar_ages = bar_ages.filter(d => d.age < 5)
  id += 1;
}
```

## Example Solution

This is an exercise in using the general update pattern. On each update, we need
to rebind the updated data array, making sure to associate each HTML tag with
the `.id` attribute in each underlying array object. We enter and append a new
rectangle at the left using `.attrs({ x: 0, y: 500 })`. Note that at this point,
the rectangle has no height -- we get the nice transition effect (bar rising to
full height) by using the update in the following block. Since the Canvas SVG
has its origin (0, 0) at the top left corner, and since the `y` coordinate of a
rectangle also corresponds to the top left corner, we set the `y` and `height`
values to,

```{r, eval = FALSE}
...
y: d => 500 - d.height,
height: d => d.height
...
```

This ensures that `y + height` is 500, so that the bottom of each rectangle is
always at `y`-coordinate 500.

HTML:
```{r, eval = FALSE}
<!DOCTYPE html>
<html>
  <head>
    <script src="https://d3js.org/d3.v7.min.js"></script>
    <script src="https://d3js.org/d3-selection-multi.v1.min.js"></script>
  </head>
  <body>
    <button id="my_button" onclick="update()">Click</button>
    <svg height=500 width=900>
    </svg>
  </body>
  <script src="q4.js"></script>
</html>
```

```{r, eval = FALSE}
let bar_ages = [],
generator = d3.randomUniform(0, 500),
id = 0;

function update() {
  bar_ages = bar_ages.map(d => { return {id: d.id, age: d.age + 1, height: d.height }})
  bar_ages.push({age: 0, height: generator(), id: id});
  bar_ages = bar_ages.filter(d => d.age < 5)
  id += 1;

  let selection = d3.select("svg")
    .selectAll("rect")
    .data(bar_ages, d => d.id)

  // Enter the new rectangle on the left
  selection.enter()
    .append("rect")
    .attrs({ x: 0, y: 500 })

  // Update all heights and locations
  d3.select("svg")
    .selectAll("rect")
    .transition()
    .duration(1000)
    .attrs({
      x: d => (900 / 5) * d.age,
      y: d => 500 - d.height,
      height: d => d.height,
      width: 100
    })

  // Exit the old rectangle on the right
  selection.exit()
    .transition()
    .duration(1000)
    .attrs({ y: 500 height: 0})
    .remove()
}
```

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q4.html" width=900 height=550 data-external="1"/>

# Transition Taxonomy

## Scoring

* a, (1 point): Correct and clearly explained choice of transition type (1
point), correct choice of transition type but with less convincing justification
(0.5 points), inappropriate choice of transition (0 points).
* b, (1 point): Correct identification of all component SVG types (1 point),
identification of most but not all SVG types (0.5 points), incorrect analysis of
SVG component types (0 points).
* c, (1 point): Complete and correct deconstruction of graphical transitions (1
point), generally correct but underdeveloped deconstruction (0.5 points),
incorrect or vague discussion of transitions (0 points).

## Question

In "Animated Transitions in Statistical Graphics," Heer and Robertson introduce
a taxonomy of visualizations transitions. These include,

  * View Transformation: We can move the "camera view" associated with a fixed
  visualization. This includes panning and zooming, for example.
  * Filtering: These transitions remove elements based on a user selection.
  For example, we may smoothly remove points in a scatterplot based on a
  dropdown menu selection.
  * Substrate Transformation: This changes the background context on which
  points lie. For example, we may choose to rescale the axis in a scatterplot
  to show a larger range.
  * Ordering: These transitions change the ordering of an ordinal variable.
  For example, we may transition between sorting rows of a heatmap
  alphabetically vs. by their row average.
  * Timestep: These transitions smoothly vary one plot to the corresponding
  plot at a different timestep. For example, we might show "slide" a time
  series to the left to introduce data for the most recent year.
  * Visualization Change: We may change the visual encoding used for a fixed
  dataset. For example, we may smoothly transition from a bar chart to a pie
  chart.
  * Data Scheme Change: This changes the features that are displayed. For
  example, we may smoothly turn a 1D point plot into a 2D scatterplot by
  introducing a new variable.
  
In this problem, we will explore how these transitions arise in practice and
explore how they may be implemented. 

## Example Solution

a. Pick any visualization from the New York Times Upshot, Washington Post
Visual Stories, the BBC Interactives and Graphics, or the Guardian
Interactives pages. Describe two transitions that it implements. Of the 7
transition types given above, which is each one most similar to? Explain
your choice.

    We will analyze the interactive map and horizon plots from [_Mapping the Spread of Drought Across the U.S._](https://www.nytimes.com/interactive/2014/upshot/mapping-the-spread-of-drought-across-the-us.html). 
Two transitions implemented in this report are,

    * Map transitions: When the reader drags a slider, they are able to see changes
in drought severity across the continental US. This exactly falls into the
"Timestep" type of transition, because it shows the same view (the drought map)
but with different underlying data as the sider is changed.
    * Horizon plot details: When the user places a mouse on the horizon plot, it
shows the exact percentage associated with that timepoint. This change is more
ambiguous, but it could be considered a visualization change, because the
underlying data have not changed, but the marks encoding them have.
Specifically, the encoding had previously only included the colors and position
on the horizon plot, but after interaction, it provides an additional bar and
text overlay to encode the same information.

b. For any transition (which may or may not be one of those you chose in
(a)), identify the types of graphical marks used to represent the data. How
would you create this type of mark in SVG?

    For the horizon plot interaction, we could use an SVG `<rect>` to draw the bar
representing the currently hovered timepoint. The height of this SVG would
reflect the severity of the drought at the current timepoint. There is also an
HTML text element that is moved on each interaction, giving the tooltip
representing the current bar's height.

c. To achieve the transition effect, how do you expect that the SVG elements
would be modified / added / removed? Specifically, if elements are modified,
what SVG `attrs` would be changed, and if elements are added or removed, how
would the enter-exit-update pattern apply? You do not need to look at the
code implementing the actual visualization, but you should give a plausible
description of how the transition could be implemented in D3.

    For the bar representing the hovered position, we would have to transition
  both the $x$-axis location and the height of the bar. There do not need to be
  any entrances or exits of HTML elements, since we are only ever showing one
  bar at a time. Roughly, we would bind data on the drought severity at the
  currently hovered year and then update the position of the bar and text that
  give details, like in the following pseudocode,
  
    ```{r, eval = FALSE}
    d3.select("#focus_bar")
      .data(current_year)
      .attrs({
        height: d => scales.drought(d.drought),
        y: d => baseline - scales.drought(d.drought),
        x: d => scales.year(d.year)
      })
    ```
    
    assuming that the object `scales` defines two linear scales mapping drought
    severity to bar height and selected year to $x$ position, respectively.
    
# Icelandic Population Analysis

## Scoring

* a, Discussion (1 point): Clear interpretation and takeaways (1 point), missing
some important aspects of interpretation (0.5 points), incorrect or
underdeveloped explanations (0 points).
* b, Discussion (1 point): Accurate and complete explanation of the filtering
and ID implementations, as well as their role in the transition (1.5 points),
accurate but potentially incomplete explanations of these steps or their role
(0.75 points), inaccurate or underdeveloped explanation (0 points).
* c, Discussion (1 point): Correct and specific explanation of the transition
effect (1 point), generally correct explanation but lacking important details
(0.5 points), incorrect explanation (0 points).
* d, Design and discussion (1 point): Creative and effective visual design
proposal (1 point), appropriate but less well-developed deisgn proposal (0.5
points), ineffective or vaguely communicated proposal (0 points).

## Question

In this problem, we will analyze the design and implementation of this [interactive visualization](https://observablehq.com/@mbostock/icelandic-population-by-age-1841-2019) of Iceland's population.


## Example Solution

a. Explain how to read this visualization. What are two potential insights a
reader could takeaway from this visualization?

    For reading the visualization, 
      * At a fixed timepoint, the visualization describes the population age
      distribution. It shows how much of the population is in different age ranges.
      It also shows which age groups have a surplus of one vs. another gender.
      * When animated, it shows how the overall population as well as the age
      distribution has shifted over time. By changing the selected year, it allows
      comparison of the age distribution and gender surplus between different
      timepoints.
      
    Example takeaways,
      * The age distribution has shifted towards an older population as time
      progresses.
      * During the 19th century, there tended to be more women than men, but this
      has reversed in the 20th century.
      * A rapid increase in the number of children born right after 1950 is visible.
      There also appears to be an increase in the number of 30 - 40 year olds in the
      2000's and 2010's, which might be a result of immigration into the country.
  
b. The implementation uses the following data join,
    
    ```{r, eval = FALSE}
    rect = rect
      .data(data.filter(d => d.year === year), d => `${d.sex}:${d.year - d.age}`)
    ```
      
    What does this code do? What purpose does it serve within the larger visualization?
    
    This binds the dataset filtered to the currently selected year. It is used
    in the general update pattern for entering, updating, and exiting bars. The
    entered bars correspond to a newly born cohort. The updates both age each
    cohort (shift the bars to the left) and change the number of individuals in
    them (update the heights of the rectangles). The exits remove the cohorts
    after they have passed age 105.
    
    The second part of the command above, `d => \`${d.sex}:${d.year - d.age}\`)`
    is an ID function. It maps each rectangle to a gender and generational
    cohort (note that `year - age` is the year of birth) combination. If it
    didn't include this ID, then the heights of the bars would change
    (reflecting the change in the population distribution), but we wouldn't see
    the transitioning of one cohort from one age group to the next.
    
c. When the bars are entered at `Age = 0`, they seem to "pop up," rather
than simply being appended to the end of the bar chart. How is this effect
implemented?

    When the bars are entered, their height is set to be zero. It is only during
    the following block that the height attribute is set to the number of
    individuals in each cohort. Since the change is implemented with an
    intermediate transition `rect.transition().attr(...`, we are able to have a
    smooth "pop up" effect for this first bar.

d. Suppose that you had comparable population-by-age data for two countries.
What queries would be interesting to support? How would you generalize the
current visualization's design to support those queries?

    Some example queries that we might be interested in are,
      * At a given point in time, how to the age distributions compare to one
      another? Which country has a larger fraction of older or younger
      individuals?
      * Do the age distributions shift differently between the two countries?
      For example, if within a certain window of years, there is a rapid influx
      of immigrants within a certain age group for country A, is there a similar
      shift in that age group for country B?

    An example design that could address these queries is to turn the current
    visualization on its side, so that births enter from the bottom and deaths
    exit near the top. Then, we can place bars for the two countries facing out
    around a central axis. We could continue using the same animation, and by
    comparing the shapes on the left and right hand sides of the display, we
    would be able to see differences in the population age structure.