---
title: "Problem Set 2 - Solutions"
output: rmdformats::readthedown
css: custom.css
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = TRUE)
```

```{r}
library(tidyverse)
library(shiny)
library(lubridate)
my_theme <- theme_bw() +
  theme(
    panel.background = element_rect(fill = "#f7f7f7"),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(),
    plot.background = element_rect(fill = "transparent", colour = NA)
  )
theme_set(my_theme)
```


# Interactive German Traffic 

## Scoring

* a - b, Design (1 points): Creative and readable (1 point), generally appropriate but with some lack of critical attention (.5 points), difficult to read (0 points)
* a - b, Code (0.5 points): Clear and concise (0.5 points), correct but unnecessarily complex (0.25 points), missing (0 points)
* c, Design and Discussion (1 points): Creative question, solution, and
interpretation (1 point), appropriate question, solution, and interpretation,
but perhaps simplistic question / difficult to read design / underdeveloped
interpretation (0.5 points), misleading design or no interpretation (0 points)
* c, Code (0.5 points): Clear and concise (0.5 points), correct but unnecessarily complex (0.25 points), missing (0 points)

## Question

This problem will revisit the previous problem from an interactive point of
view. We will build a visualization that helps users explore daily traffic
patterns across multiple German cities, using interactivity to help users
navigate the collection. We will need additional features related to the day of
the week for each timepoint, created by the `wday` function below,

```{r}
traffic <- read_csv("https://uwmadison.box.com/shared/static/x0mp3rhhic78vufsxtgrwencchmghbdf.csv") %>%
 mutate(day_of_week = wday(date))
```


## Example Solution

a. Design and implement a Shiny app that allows users to visualize traffic
over time across selected subsets of cities. Make sure that it is possible
to view data from more than one city at a time. It is not necessary to label
the cities within the associated figure.

```{r, eval = FALSE}
plot_traffic <- function(df) {
  ggplot(df) +
    geom_line(aes(date, value, group = name)) +
    labs(x = "Date", y = "Traffic") +
    theme(axis.title = element_text(size = 20))
}

ui <- fluidPage(
  selectInput("city", "City", unique(traffic$name), multiple = TRUE),
  plotOutput("time_series")
)

server <- function(input, output) {
  output$time_series <- renderPlot({
    traffic %>%
      filter(name %in% input$city) %>%
      plot_traffic()
  })
}

shinyApp(ui, server)
```

<iframe src="https://data-viz.it.wisc.edu/content/da978e9a-126c-4319-abcf-ce5b3fefadc3" width=900 height=550 data-external="1"/>

b. Introduce new inputs to allow users to select a contiguous range of days
of the week. For example, the user should have a way of zooming into the
samples taken within the Monday - Wednesday range.

```{r, eval = FALSE}
ui <- fluidPage(
  selectInput("city", "City", unique(traffic$name), multiple = TRUE),
  sliderInput("day_of_week", "Days", 2, 7, c(2, 7)),
  plotOutput("time_series")
)

server <- function(input, output) {
  output$time_series <- renderPlot({
    traffic %>%
      filter(
        name %in% input$city, 
        day_of_week >= input$day_of_week[1] & day_of_week <= input$day_of_week[2]
      ) %>%
      plot_traffic()
  })
}

shinyApp(ui, server)
```

<iframe src="https://data-viz.it.wisc.edu/content/aa7c25b0-618f-41a2-80b7-1816c6ea9b41" width=900 height=550 data-external="1"/>

c. Propose, but do not implement, at least one alternative strategy for
supporting user queries from either part (a) or (b). What are the tradeoffs
between the different approaches in terms of visual effectiveness and
implementation complexity?

# NYC Rentals

## Scoring

## Question

In this problem, we'll create a visualization to dynamically query a
[dataset](https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv)
of Airbnb rentals in Manhattan in 2019. The steps below guide you through the
process of building this visualization.

## Example Solution

a. Make a scatterplot of locations (Longitude vs. Latitude) for all the rentals,
colored in by `room_type`.

```{r}
rentals <- read_csv("https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv")
ggplot(rentals) +
  geom_point(aes(longitude, latitude, col = room_type), size = 0.3, alpha = 0.6) +
  scale_color_manual(values = c("#3F4B8C","#F26444", "#40331D")) +
  guides(col = guide_legend(override.aes = list(alpha = 1, size = 2))) +
  labs(col = "Room Type") +
  coord_fixed() +
  theme_void()
```

b. Design a plot and a dynamic query so that clicking or brushing on the
plot updates the points that are highlighted in the scatterplot in (a). For
example, you may query a histogram of prices to focus on neighborhoods that
are more or less affordable.

```{r, eval = FALSE}
ui <- fluidPage(
  h3("NYC Airbnb Rentals"),
  fluidRow(
    column(6,
           plotOutput("histogram", brush = brushOpts("plot_brush", direction = "x"), height = 200),
           dataTableOutput("table")
    ),
    column(6, plotOutput("map", height = 600)),
  ),
  theme = bs_theme(bootswatch = "minty")
)

server <- function(input, output) {
  selected <- reactiveVal(rep(TRUE, nrow(rentals)))
  observeEvent(input$plot_brush, {
    selected(brushedPoints(rentals, input$plot_brush, allRows = TRUE)$selected_)
  })
  
  output$histogram <- renderPlot(overlay_histogram(rentals, selected()))
  output$map <- renderPlot(scatterplot(rentals, selected()))
  output$table <- renderDataTable(filter_df(rentals, selected()))
}

shinyApp(ui, server)
```

```{r, eval = FALSE}

scatterplot <- function(df, selected_) {
  df %>%
    mutate(selected = selected_) %>%
    ggplot() +
    geom_point(
      aes(
        longitude, latitude, col = room_type, 
        alpha = as.numeric(selected),
        size = as.numeric(selected)
      )
    ) +
    scale_color_manual(values = c("#3F4B8C","#F26444", "#40331D"), guide = "none") +
    scale_alpha(range = c(0.1, .5), guide = "none") +
    scale_size(range = c(0.1, .9), guide = "none") +
    coord_fixed() +
    theme_void()
}

overlay_histogram <- function(df, selected_) {
  sub_df <- filter(df, selected_)
  ggplot(df, aes(trunc_price, fill = room_type)) +
    geom_histogram(alpha = 0.3, binwidth = 25) +
    geom_histogram(data = sub_df, binwidth = 25) +
    scale_y_continuous(expand = c(0, 0, 0.1, 0)) +
    scale_fill_manual(values = c("#3F4B8C","#F26444", "#40331D")) +
    labs(
      fill = "Room Type",
      y = "Count",
      x = "Price"
    )
}

filter_df <- function(df, selected_) {
  filter(df, selected_) %>%
    select(name, price, neighbourhood, number_of_reviews) %>%
    rename(Name = name, Price = price, Neighborhood = neighbourhood, `Number of Reviews` = number_of_reviews)
}
```


<iframe src="https://data-viz.it.wisc.edu/content/b31a14ea-20dd-4718-b2e9-39bc318a2306" width=900 height=550 data-external="1"/>

c. Implement the reverse graphical query. That is, allow the user to update
the plot in (b) by brushing over the scatterplot in (a).

```{r eval = FALSE}
ui <- fluidPage(
  h3("NYC Airbnb Rentals"),
  fluidRow(
    column(6,
           plotOutput("histogram", brush = brushOpts("plot_brush", direction = "x"), height = 200),
           dataTableOutput("table")
    ),
    column(6, plotOutput("map", brush = "plot_brush", height = 600)),
  ),
  theme = bs_theme(bootswatch = "minty")
)
```

<iframe src="https://data-viz.it.wisc.edu/content/a410cc0e-84a1-46f6-959d-1c8cfbb2c729" width=900 height=550 data-external="1"/>

d. Comment on the resulting visualization(s). If you had a friend who was
interested in renting an Airbnb in NYC, what would you tell them?
    

# Random Point Transitions

## Scoring

## Question
This exercise will give practice implementing
transitions on simulated data. The code below generates a random set of 10
numbers,

```{d3, eval = FALSE}
let generator = d3.randomUniform();
let x = d3.range(10).map(generator);
```

## Example Solution

a. Encode the data in `x` using the x-coordinate positions of 10 circles.


<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3a.html" width=900 height=550 data-external="1"/>


b. Animate the circles. Specifically, at fixed time intervals, generate a
new set of 10 numbers, and smoothly transition the original set of circles
to locations corresponding to these new numbers.


<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3b.html" width=900 height=550 data-external="1"/>


c. Extend your animation so that at least one other attribute is changed at
each time step. For example, you may consider changing the
color or the size of the circles. Make sure that transitions remain smooth
(e.g., if transitioning size, gradually increase or decrease the circles'
radii).

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q3c.html" width=900 height=550 data-external="1"/>

# Bar Chart Transitions

## Scoring

## Question

This problem continues [Simple Bar Chart] above. We will create a bar chart that
adds and removes one bar each time a button is clicked. Specifically, the
function below takes an initial array `x` and creates a new array that removes
the first element and adds a new one to the end. Using D3’s generate update
pattern, write a function that updates the visualization from [Simple bar chart]
every time that `update_data()` is called. New bars should be entered from the
left, exited from the right, and transitioned after each click. Your solution
should look (roughly) like [this example](https://github.com/krisrs1128/stat679_code/blob/main/activities/week5/simple_bars_example.mov?raw=true).

```{d3, eval = FALSE}
let bar_ages = [],
generator = d3.randomUniform(0, 500),
id = 0;

function update() {
  bar_ages = bar_ages.map(d => { return {id: d.id, age: d.age + 1, height: d.height }})
  bar_ages.push({age: 0, height: generator(), id: id});
  bar_ages = bar_ages.filter(d => d.age < 5)
  id += 1;
}
```

## Example Solution

```{r, eval = FALSE}
<!DOCTYPE html>
<html>
  <head>
    <script src="https://d3js.org/d3.v7.min.js"></script>
    <script src="https://d3js.org/d3-selection-multi.v1.min.js"></script>
  </head>
  <body>
    <button id="my_button" onclick="update()">Click</button>
    <svg height=500 width=900>
    </svg>
  </body>
  <script src="q4.js"></script>
</html>
```

```{r, eval = FALSE}
let bar_ages = [],
generator = d3.randomUniform(0, 500),
id = 0;

function update() {
  bar_ages = bar_ages.map(d => { return {id: d.id, age: d.age + 1, height: d.height }})
  bar_ages.push({age: 0, height: generator(), id: id});
  bar_ages = bar_ages.filter(d => d.age < 5)
  id += 1;

  let selection = d3.select("svg")
    .selectAll("rect")
    .data(bar_ages, d => d.id)

  // Enter the new rectangle on the left
  selection.enter()
    .append("rect")
    .attrs({ x: 0, y: 500 })

  // Update all heights and locations
  d3.select("svg")
    .selectAll("rect")
    .transition()
    .duration(1000)
    .attrs({
      x: d => (900 / 5) * d.age,
      y: d => 500 - d.height,
      height: d => d.height,
      width: 100
    })

  // Exit the old rectangle on the right
  selection.exit()
    .transition()
    .duration(1000)
    .attrs({ y: 500 height: 0})
    .remove()
}
```

<iframe src="https://krisrs1128.github.io/stat679_code/exercises/ps2/q4.html" width=900 height=550 data-external="1"/>

# Transition Taxonomy

## Scoring

## Question

In "Animated Transitions in Statistical Graphics," Heer and Robertson introduce
a taxonomy of visualizations transitions. These include,

  * View Transformation: We can move the "camera view" associated with a fixed
  visualization. This includes panning and zooming, for example.
  * Filtering: These transitions remove elements based on a user selection.
  For example, we may smoothly remove points in a scatterplot based on a
  dropdown menu selection.
  * Substrate Transformation: This changes the background context on which
  points lie. For example, we may choose to rescale the axis in a scatterplot
  to show a larger range.
  * Ordering: These transitions change the ordering of an ordinal variable.
  For example, we may transition between sorting rows of a heatmap
  alphabetically vs. by their row average.
  * Timestep: These transitions smoothly vary one plot to the corresponding
  plot at a different timestep. For example, we might show "slide" a time
  series to the left to introduce data for the most recent year.
  * Visualization Change: We may change the visual encoding used for a fixed
  dataset. For example, we may smoothly transition from a bar chart to a pie
  chart.
  * Data Scheme Change: This changes the features that are displayed. For
  example, we may smoothly turn a 1D point plot into a 2D scatterplot by
  introducing a new variable.
  
In this problem, we will explore how these transitions arise in practice and
explore how they may be implemented. 

## Example Solution

a. Pick any visualization from the New York Times Upshot, Washington Post
Visual Stories, the BBC Interactives and Graphics, or the Guardian
Interactives pages. Describe two transitions that it implements. Of the 7
transition types given above, which is each one most similar to? Explain
your choice.
b. For any transition (which may or may not be one of those you chose in
(a)), identify the types of graphical marks used to represent the data. How
would you create this type of mark in SVG?
c. To achieve the transition effect, how do you expect that the SVG elements
would be modified / added / removed? Specifically, if elements are modified,
what SVG `attrs` would be changed, and if elements are added or removed, how
would the enter-exit-update pattern apply? You do not need to look at the
code implementing the actual visualization, but you should give a plausible
description of how the transition could be implemented in D3.

# Icelandic Population Analysis

## Scoring

## Question

In this problem, we will analyze the design and implementation of this [interactive visualization](https://observablehq.com/@mbostock/icelandic-population-by-age-1841-2019) of Iceland's population.


## Example Solution

a. Explain how to read this visualization. What are two potential insights a
reader could takeaway from this visualization?
b. The implementation uses the following data join,
    
    ```{r, eval = FALSE}
    rect = rect
      .data(data.filter(d => d.year === year), d => `${d.sex}:${d.year - d.age}`)
    ```
      
    What does this code do? What purpose does it serve within the larger visualization?
    
c. When the bars are entered at `Age = 0`, they seem to "pop up," rather
than simply being appended to the end of the bar chart. How is this effect
implemented?
d. Suppose that you had comparable population-by-age data for two countries.
What queries would be interesting to support? How would you generalize the
current visualization's design to support those queries?


