---
title: Manipulating Graph Data
layout: post
output: 
  md_document:
    preserve_yaml: true
---

_Reading and modifying graph data_

```{r, echo = FALSE}
library(knitr)
opts_knit$set(base_dir = "/", base.url = "/")
opts_chunk$set(
  warning = FALSE, 
  message = FALSE,
  fig.path = "stat679_notes/assets/week9-1/"
  )
```

```{r}
library(tidygraph)
library(ggraph)
```


1. Before diving into graph data visualization, let’s get some experience
manipulating graphs hands on.

1. The goal of the tidygraph package is to extend the semantics of the tidyverse
to graph-structured data. This is necessary because any graph is represented by
two data structures, a set of nodes and a set of edges.

1. This can be usefully organized as a pair of `data.frames`, and the
`tidygraph` structure represents graphs in exactly this way.
For example, `G` below is a tidy graph structure showing the friendship
connections between 70 students in a high school over two years.

```{r}
G <- as_tbl_graph(highschool)
G
```


1. The beauty of this data structure is that we can define the analogs of the
usual tidyverse verbs for it. For example, we can derive a new node attribute
using `mutate`.

    ```{r}
    G %>%
      mutate(favorite_color = sample(c("red", "blue"), n(), replace = TRUE))
    ```

1. What if we want to mutate the edges instead? We have to tell tidygraph to
“activate” the edge set,
    
    ```{r}
    G %>%
      activate(edges) %>%
      mutate(weight = runif(n()))
    ```
    
  To avoid these activate calls, a convenient shorthand is calling mutate with
  `%N>%` and `%E>%`.
  
    ```{r}
    G %E>%
      mutate(weight = runif(n()))
    ```
      
1. There are many other verbs that have been defined for tidygraph objects. For
example, we can join two graphs together.

    ```{r}
    G1 <- create_ring(10)  %N>%
      mutate(id = LETTERS[1:n()])
    G2 <- create_bipartite(4, 2) %>%
      mutate(id = LETTERS[1:n()])
    G1 %>%
      graph_join(G2)
    ```
    
```{r, echo = FALSE}
ggraph(G1) +
  geom_edge_link() +
  geom_node_label(aes(label = id))
  
ggraph(G2) +
  geom_edge_link() +
  geom_node_label(aes(label = id))
  
ggraph(G1 %>% graph_join(G2)) +
  geom_edge_link() +
  geom_node_label(aes(label = id))
```
    
1. Similarly, we can filter nodes or edges based on their attributes.

    ```{r}
    G %E>%
      mutate(weight = runif(n())) %>%
      filter(weight < 0.2) %>%
      arrange(-weight)
    ```
    
1. It’s possible to perform simple graph algorithms using these verbs. For
example, we can cluster nodes based on their connection structure.

```{r}
G %>%
  to_undirected() %>%
  mutate(cluster = group_louvain())
```

```{r}
G %>%
  to_undirected() %>%
  mutate(cluster = group_louvain()) %>%
  ggraph() +
  geom_edge_link(width = 0.2) +
  geom_node_point(aes(col = as.factor(cluster)), size = 3) +
  scale_color_brewer(palette = "Set2")
```

1. We can even map over nodes to compute topological queries. For example, the
block below computes the number of neighbors within two step of each node, using
the `map_nodes` function.

    ```{r}
    G %>%
      mutate(two_steps = local_size(order = 2))
    ```
  
