---
title: Visualizing Distributions
layout: post
output: 
  md_document:
    preserve_yaml: true
---

_Short description_

```{r, echo = FALSE}
library(knitr)
opts_knit$set(base_dir = "/", base.url = "/")
opts_chunk$set(
  warning = FALSE, 
  message = FALSE,
  fig.path = "stat679_notes/assets/week13-2/"
)
```

```{r}
library(tidyverse)
library(ggdist)
library(distributional)
library(patchwork)
theme_set(theme_bw())
```

1. In the last notes, we recommended frequency framing plots as a default
approach for visualizing uncertainty. If you have ever skimmed through
scientific publications, though, you might have been surprised by this choice —
in technical literature, the overwhelming majority of uncertainty visualizations
are based on error bars.

1. In many of these publications, frequency framing would likely be prefereable,
because they give a richer view of the distribution of possible outcomes.
However, there are three scenarios where error bars are hard to beat: when we
need to compactly represent uncertainty for many units and when we want to
combine them with other plots.

3. Since error bars take up so little space, they can be included in highly
information dense views. For example, below, we stack 95% confidence intervals
for 50 means.

1. Since they are so compact, it is relatively easy to incorporate error bars
into other visualizations. For example, we can replace points in a scatterplot
with crosses that summarize uncertainty in each dimension.

1. One difficulty with error bars is that their interpretations are not
self-evident from their appearance — they need to be included in the title or
caption to the figure. For example, 90 and 99% confidence intervals have
different meanings, and this needs to be explained clearly.

1. A variation on error bars that pack a little more information in nearly as
little space is the graded error bar. This is a type of error bar where
different levels of thickness are matched with different interpretations. In the
example below, we are simultaneously showing 90, 95, and 99% confidence
intervals for a mean.

1. These graded error bars can be combined with distribution plots to create eye
or half-eye plots. This approach benefits from the advantages of both the
distribution and graded error approaches. From the distribution component, we
can see the full distribution of uncertainty, not simply summaries. Using the
error bar, we can tell whether specific values are above or below important
cutoffs.

1. A related approach is to fill in subsets of a distribution plot according to
more interpretable cutoffs.

1. Two other encodings are worth knowing, but are harder to fit into the rest of
this discussion. In interval plots, the fill opacity is used to encode
probability. It is harder to evaluate the exact probability values, since fill
is harder to read than position, but it is a more compact representation than
full distribution plots.

1. A second encoding is the complementary cumulative distribution (CCDF) plot.
It represents the probability that the data will lie above a particular value.
Some studies have found that nontechnical audiences often have better inferences
when they are presented distributional uncertainty via CCDFs.
